Verifying Demonstrations

### 2018-11-15 paper/analysis-performance.tex
s/PRIVO/CROCUS/g

\subsection{Smartphones, smartcards}
Performance considerations are crucial during the protests due to the nature of the devices used to run \PRIVO, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity. 
Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}. 
However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.

>>>>

\subsection{Smartphones, smartcards}
Performance considerations are crucial during the protests due to the nature of the devices used to run \CROCUS, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity. 
Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}. 
However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.

### 2018-11-15 paper/intro.tex
s/PRIVO/CROCUS/g

The paper is organized as follows.
First, in \cref{system-model}, we formalize the notion of protest and define the desired verifiability properties.
We also present our system as well as the adversary model together with desired privacy properties.
Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \PRIVO. 
In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
%\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
%Seb: we need to be careful about the above sentence
This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then \cref{Protocol}, we present \PRIVO, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}

>>>>

The paper is organized as follows.
First, in \cref{system-model}, we formalize the notion of protest and define the desired verifiability properties.
We also present our system as well as the adversary model together with desired privacy properties.
Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS. 
In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
%\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
%Seb: we need to be careful about the above sentence
This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}

### 2018-11-15 paper/protocol.tex
s/PRIVO/CROCUS/g

\section{\PRIVO:\@ A protocol for crowd counting estimation}%
\label{Protocol}

We now present \PRIVO, a protocol for securely and privately verifying crowd counts.
The protocol consists of five phases: setup, join, participation, submission and verification phases.
The setup is described in \cref{ProtocolSetup}.
The join, participation and submission phases are detailed in \cref{ProtocolDuring}.
Finally, the verification phase is presented in \cref{ProtocolVerification}.

@@

\emph{Setup: \((\spk, \ssk)\gets \PRIVOsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
Let \(G = \gen g\) be a group with generator \(g\) and of prime order \(q\).
Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
}.
Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).

\emph{Registration: \(\sk\gets 
    \Proto{\PRIVOreg[_P][\spk]}{\PRIVOreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key and 
obtains a signature on it by the \ac{CA} but without revealing it to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
The participant acts as prover and the \ac{CA} as verifier while they perform 
the following \ac{ZKPK} protocol:
\[
  \PK[k,r][M = g^k Z^r].
\]
If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = g^a\).
Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, 
  C = A^x M^{axy})\) and sends it to the participant.
The participant then verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
\end{align*}
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \PRIVOjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (in 
\cref{fig:ProofFig,fig:ProtocolOverview}).
More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, k, r)\)).
The protester should also receive a time-correlated random value from the time-stamping service, \(t_s\gets \TSget\).

@@

\begin{figure}
  \centering
  \small
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
    permanent storage \(S\). Note that \pid always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure}

\emph{Joining as a witness: \(t_s'\gets \PRIVOjoin_W\).}
The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
set the start of the time interval of creation for the proof share.

\emph{Participation: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The protester sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the protester and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the protester as the prover 
and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k_P+\cid)} \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows.
(Remember that this \ac{PK} should be run as the \ac{PPK} in 
\cref{DB-anon-cred} and repeated multiple times to achieve security.)
The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the protester computes
\begin{align*}
  s_k &= -ck + r_k, \\
  s_r &= -cr + r_r, \\
  s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
  = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the protester.
As a consequence, both the protester and the witness have the tuple \(\psh = 
  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
protester (\cref{fig:ProofFig}).

\emph{Submission: \(\psh_P\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.
The protester computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the 
correctness of \(\pid\).
More specifically,
\begin{multline*}
  \pi_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
    \begin{aligned}
      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the protester uploads the tuple \[  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})\] for permanent storage.

\emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
(This is to make the time interval as early as possible, whoever is the faster 
will submit it.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{\wid}\) as follows:
\begin{multline*}
  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[ \psh_W = (\cid, \pid, \wid, t_s, 
  t_s', t_e', l, \pi_{\wid}) \] for permanent storage.

>>>>

\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\label{Protocol}

We now present \CROCUS, a protocol for securely and privately verifying crowd counts.
The protocol consists of five phases: setup, join, participation, submission and verification phases.
The setup is described in \cref{ProtocolSetup}.
The join, participation and submission phases are detailed in \cref{ProtocolDuring}.
Finally, the verification phase is presented in \cref{ProtocolVerification}.

@@

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
Let \(G = \gen g\) be a group with generator \(g\) and of prime order \(q\).
Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
}.
Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key and 
obtains a signature on it by the \ac{CA} but without revealing it to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
The participant acts as prover and the \ac{CA} as verifier while they perform 
the following \ac{ZKPK} protocol:
\[
  \PK[k,r][M = g^k Z^r].
\]
If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = g^a\).
Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, 
  C = A^x M^{axy})\) and sends it to the participant.
The participant then verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
\end{align*}
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (in 
\cref{fig:ProofFig,fig:ProtocolOverview}).
More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, k, r)\)).
The protester should also receive a time-correlated random value from the time-stamping service, \(t_s\gets \TSget\).

@@

\begin{figure}
  \centering
  \small
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of the Join, Participation and Submission phases of \CROCUS.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
    permanent storage \(S\). Note that \pid always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure}

\emph{Joining as a witness: \(t_s'\gets \CROCUSjoin_W\).}
The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
set the start of the time interval of creation for the proof share.

\emph{Participation: \(\pi\gets
    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The protester sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the protester and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the protester as the prover 
and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k_P+\cid)} \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows.
(Remember that this \ac{PK} should be run as the \ac{PPK} in 
\cref{DB-anon-cred} and repeated multiple times to achieve security.)
The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the protester computes
\begin{align*}
  s_k &= -ck + r_k, \\
  s_r &= -cr + r_r, \\
  s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
  = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the protester.
As a consequence, both the protester and the witness have the tuple \(\psh = 
  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
protester (\cref{fig:ProofFig}).

\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.
The protester computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the 
correctness of \(\pid\).
More specifically,
\begin{multline*}
  \pi_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
    \begin{aligned}
      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the protester uploads the tuple \[  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})\] for permanent storage.

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
(This is to make the time interval as early as possible, whoever is the faster 
will submit it.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{\wid}\) as follows:
\begin{multline*}
  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[ \psh_W = (\cid, \pid, \wid, t_s, 
  t_s', t_e', l, \pi_{\wid}) \] for permanent storage.
